Performance of prediction models for opportunities for improvment in trauma care among women compared to men and across patient cohorts

### 2023-12-12 manuscript.Rmd
attempt 2 solving merge conflict
Update table 1 and save as word file

---
title: "Performance of prediction models for opportunities for improvment in trauma care among women compared to men and across patient cohorts"
author: "Anna Thoss"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

```{r tab1, echo=FALSE, fig.cap="Selected sample characteristics", fig.align='center' }
if (output.format == "latex") {
  tab1 <- t1kable(create.tableone(dataset), "latex", longtable = T, booktabs = T) %>%
    kable_styling(latex_options = c("repeat_header", "condensed"), repeat_header_text = "(cont.)", font_size = 8) %>%
    kableExtra::footnote(general = "\\\\textit{Definition of  abbreviations:} OFI = Opportunity for Improvement; ED = Emergency Department; GCS = Glascow Coma Scale.\\\\newline Time to first CT and Time to definitive treatment: Measured in minutes from arrival at the hospital.", general_title = "",threeparttable =  TRUE, escape = FALSE)
} else if (output.format == "docx") {
    tab1 <- t1flex(create.tableone(dataset)) %>%
      add_footer_lines("OFI = Opportunity for Improvement; ED = Emergency Department; GCS = Glascow Coma Scale.\n Time to first CT and Time to definitive treatment: Measured in minutes from arrival at the hospital.") %>%
      autofit()
}

>>>>

---
title: "Performance of prediction models for opportunities for improvment in trauma care among women compared to men and across patient cohorts"
author: "Anna Thoss"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

```{r tab1, echo=FALSE, fig.cap="Selected sample characteristics", fig.align='center' }
if (output.format == "latex") {
  tab1 <- t1kable(create.tableone(dataset), "latex", longtable = T, booktabs = T) %>%
    kable_styling(latex_options = c("repeat_header", "condensed"), repeat_header_text = "(cont.)", font_size = 8) %>%
    kableExtra::footnote(general = "\\\\textit{Definition of  abbreviations:} OFI = Opportunity for Improvement; ED = Emergency Department; GCS = Glascow Coma Scale.\\\\newline Time to first CT and Time to definitive treatment: Measured in minutes from arrival at the hospital.", general_title = "",threeparttable =  TRUE, escape = FALSE)
} else if (output.format == "docx") {
    tab1 <- t1flex(create.tableone(dataset)) %>%
      add_footer_lines("OFI = Opportunity for Improvement; ED = Emergency Department; GCS = Glascow Coma Scale.") %>%
      autofit()
}
